---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r,echo=FALSE, message=FALSE}
devtools::load_all()
```

# DNAplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/brunomioto/DNAplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brunomioto/DNAplot/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/brunomioto/DNAplot/branch/master/graph/badge.svg)](https://app.codecov.io/gh/brunomioto/DNAplot?branch=master)
<!-- badges: end -->

The DNAplot package provides a simple and customizable function to create aesthetically pleasing plots of DNA sequences. Each base is represented by a colored rectangle, allowing for easy visualization and analysis of sequence features.

## Installation

You can install the development version of DNAplot from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("brunomioto/DNAplot")
```

## Get started

```{r example}
library(DNAplot)
```

Just write a sequence and plot it!

```{r, fig.width = 9, fig.height = 1, dpi=600}
sequence <- "ACTGAAGTA"

plot_dna(sequence)
```

You can also plot undefined bases

```{r, fig.width = 9, fig.height = 1, dpi=600}
sequence <- "ACYGARGTA"

plot_dna(sequence)
```
